An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
small errors

After first oversegmenting the word, we will recover the original character through postprocessing steps combining different word segments.

\subsection{Normalization}
The first action is again normalizing the word image.
We will resuze the image to a fixed height of $100px$.
This will result in more consistency in rule-based post processing steps.

@@

\subsection{Skeletonization}
Now we will skeletonize our word image.
This will normalize the thickness of the strokes to a single pixel.
This allows us to execute our Verical projection profile and interpret the results easily.
The skeletonization algorithm used is the Zhang Suen thinning algorithm \cite{zsthinning}.

>>>>

After first oversegmenting the word, we recover the original character through postprocessing steps combining different word segments.

\subsection{Normalization}
The first action is again normalizing the word image.
We resize the image to a fixed height of $100px$.
This result in more consistency in rule-based postprocessing steps.

@@

\subsection{Skeletonization}
Now we skeletonize our word image.
This normalizes the thickness of the strokes to a single pixel.
This allows us to execute our Verical projection profile and interpret the results easily.
The skeletonization algorithm used is the Zhang Suen thinning algorithm \cite{zsthinning}.
